---
title: "Installing renv"
author: ""
date: ""
format:
  html:
    code-fold: true
    toc: true
---

# Introduction

`renv` is a package for managing R dependencies. It helps ensure reproducibility by isolating project-specific package environments.

# Steps to Install and Initialize `renv`

## Step 1: Install `renv` Package

```{r}
install.packages("renv")
```

This command installs the `renv` package from CRAN.

## Step 2: Initialize `renv`

```{r}
renv::init()
```

-   This initializes an `renv` environment in your project.
-   A `renv.lock` file is created, which records the state of your library.
-   A `renv` folder is created in your project directory to store the environment.

## Step 3: Install Project-Specific Dependencies

Install the required packages for your project:

```{r}
install.packages("yaml")
```

Replace `<package_name>` with the packages your project needs.

## Step 4: Snapshot the Environment

```{r}
renv::snapshot()
```

This command updates the `renv.lock` file with the current state of your environment, ensuring reproducibility.

```{r}
renv::dependencies()
```

# Conclusion

`renv` simplifies dependency management in R projects, promoting consistency and reproducibility. Regularly snapshot your environment to keep the `renv.lock` file updated.
