---
title: "Restore Project Environment"
author: "Your Name"
format: html
---

# Environment Restoration

This document will restore both R and Python environments using renv.

## Restore Environments

```{r}
#| warning: false
#| message: false

# Restore both R and Python environments from renv.lock
renv::restore()
```

## Verify Setup

### R Environment Status

```{r}
#| warning: false
#| message: false

# Check R environment status
cat("R Version:", R.version$version.string, "\n\n")
cat("R Environment Status:\n")
renv::status()
```

### Python Environment Status

```{python}
#| warning: false

import sys
import pkg_resources
from tabulate import tabulate

# Print Python version
print(f"Python Version: {sys.version.split()[0]}")

# Get all installed packages
packages = sorted([
    [pkg.key, pkg.version]
    for pkg in pkg_resources.working_set
])

# Display all packages
print("\nInstalled Python Packages:")
print(tabulate(packages, headers=['Package', 'Version'], tablefmt='pipe'))
```

## Next Steps

If everything is set up correctly:

1. All required R packages should be installed and available
2. The Python virtual environment should be activated and packages installed
3. You can now proceed to work with other Quarto documents in this project

If you encounter any issues:

1. Check the error messages in the output above
2. Refer to the Troubleshooting section in the README
3. Try re-running this document
