---
title: "Restore Project Environment"
author: "Your Name"
format: html
---

# Environment Restoration

This document will:
1. Restore R packages using renv
2. Activate Python virtual environment
3. Verify the setup

## Restore R Environment

First, let's restore the R environment using renv:

```{r}
#| warning: false
#| message: false

# Restore R packages from renv.lock
renv::restore()

```

## Activate Python Environment

Now, let's ensure the Python environment is properly configured:

```{r}
#| warning: false
#| message: false

# Read Python configuration
python_config <- jsonlite::read_json("python-config.json")

# Use Python from virtual environment
renv::use_python(
  python = file.path(getwd(), python_config$virtualenv, "bin/python"),
  type = "virtualenv"
)

# Verify Python configuration
py_config <- reticulate::py_config()
message("\nPython Configuration:")
message("- Python Version: ", py_config$version)
message("- Python Path: ", py_config$python)
message("- Virtual Environment: ", python_config$virtualenv)
```

## Verify Setup

### R Environment Status

```{r}
#| warning: false
#| message: false

# Check R environment status
cat("R Version:", R.version$version.string, "\n\n")
cat("R Environment Status:\n")
renv::status()
```

### Python Environment Status

```{python}
#| warning: false

import sys
import pkg_resources
from tabulate import tabulate

# Print Python version
print(f"Python Version: {sys.version.split()[0]}")

# Read direct dependencies from requirements.txt
with open('requirements.txt', 'r') as f:
    direct_deps = [line.strip().split('==')[0] for line in f if line.strip()]

# Get all installed packages
all_packages = sorted([
    [pkg.key, pkg.version]
    for pkg in pkg_resources.working_set
])

# Split into direct and indirect dependencies
direct_packages = []
indirect_packages = []

for pkg_name, version in all_packages:
    if pkg_name in direct_deps:
        direct_packages.append([pkg_name, version])
    else:
        indirect_packages.append([pkg_name, version])

# Display direct dependencies
print("\nDirect Python Dependencies (from requirements.txt):")
print(tabulate(sorted(direct_packages), headers=['Package', 'Version'], tablefmt='pipe'))

# Display indirect dependencies
print("\nIndirect Python Dependencies (installed as dependencies of direct packages):")
print(tabulate(sorted(indirect_packages), headers=['Package', 'Version'], tablefmt='pipe'))
```

## Next Steps

If everything is set up correctly:

1. All required R packages should be installed and available
2. The Python virtual environment should be activated and packages installed
3. You can now proceed to work with other Quarto documents in this project

If you encounter any issues:

1. Check the error messages in the output above
2. Refer to the Troubleshooting section in the README
3. Try re-running this document

## Environment Information

This section provides detailed information about your environment setup:

```{r}
#| warning: false
#| message: false

# Show R package information
cat("\nR Package Information:\n")
renv::dependencies()

# Show Python configuration
cat("\nPython Configuration:\n")
reticulate::py_config()
```
